---
title: "Data preparation BBMO"
author: "Thomas Finet"
date: "04/11/2021"
output: html_document
---

```{r}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(dplyr)
library(ggplot2)
library(stringr)
library(tidyverse)
library(openxlsx)
library(readxl)
library(vegan)
```


## Syndiniales data importation

Import abundance matrix of Connected Components (CCs) and metadata in order to extract the information related to the BBMO Temporal Series.

```{r}
CC_abund_Synd_BBMO <- read.csv("CC_abund_Synd.csv",h=T, sep=",")
Metadata_all <- read.csv("Metadata_all_1211.csv",h=T, sep=",")
Metadata_BBMO<-Metadata_all %>% filter(Dataset=='Blanes')
#We remove the first column
Metadata_BBMO<-Metadata_BBMO[,-1]
```

## Creation of data-frame

```{r}
# We select the samples that the belong to the BBMO time series
CC_abund_Synd_BBMO_clean<-select(CC_abund_Synd_BBMO, starts_with("BBMO"))
# Addition of CC ids and genus status info
CC_abund_Synd_BBMO_clean$CC_id<-CC_abund_Synd_BBMO$CC_id
CC_abund_Synd_BBMO_clean$Genus_status<-CC_abund_Synd_BBMO$Genus_status
# Set CC ids as row names
rownames(CC_abund_Synd_BBMO_clean)<-CC_abund_Synd_BBMO_clean$CC_id
# Remove CC id and X columns
CC_abund_Synd_BBMO_clean<-subset(CC_abund_Synd_BBMO_clean, select = -c(CC_id))
# Transpose table
CC_abund_Synd_BBMO_clean<-t(CC_abund_Synd_BBMO_clean)
CC_abund_Synd_BBMO_clean<-as.data.frame(CC_abund_Synd_BBMO_clean)
# Save genus status info and remove from abundance table
Status<-CC_abund_Synd_BBMO_clean[321,]
CC_abund_Synd_BBMO_clean<-CC_abund_Synd_BBMO_clean[-321,]

# Set rownames as column "Sample"
CC_abund_Synd_BBMO_clean<-rownames_to_column(CC_abund_Synd_BBMO_clean, var="Sample")
#Remove the thick after the name of the sample
Metadata_BBMO$Sample<-substr(Metadata_BBMO$Sample,1,nchar(Metadata_BBMO$Sample)-1)
#Same sample name format between metadata and abundance table 
CC_abund_Synd_BBMO_clean$Sample<-str_sub(CC_abund_Synd_BBMO_clean$Sample,5)
# Set abundance values to numeric type
CC_abund_Synd_BBMO_clean[,2:length(CC_abund_Synd_BBMO_clean)]<-sapply(CC_abund_Synd_BBMO_clean[,2:length(CC_abund_Synd_BBMO_clean)],as.numeric)
```
Same format now


Check if there are samples with null abundance

```{r}
# Calculate sum of abundance per sample
CC_abund_Synd_BBMO_clean$Sum<-rowSums(CC_abund_Synd_BBMO_clean[2:length(CC_abund_Synd_BBMO_clean)])
# Extract samples with total abundance = 0
null_samples<-subset(CC_abund_Synd_BBMO_clean,Sum==0)
print(null_samples$Sample)
# Remove Sum column
CC_abund_Synd_BBMO_clean<-subset(CC_abund_Synd_BBMO_clean, select=-c(Sum))
```

Check if there are Connected Components with null abundances

```{r}
# Compute sums of CCs abundance
CC_sum<-colSums(CC_abund_Synd_BBMO_clean[2:length(CC_abund_Synd_BBMO_clean)])
# Set Sample column as rownames, remove Sample column and add of Sum row
rownames(CC_abund_Synd_BBMO_clean)<-CC_abund_Synd_BBMO_clean$Sample
CC_abund_Synd_BBMO_clean_2<-subset(CC_abund_Synd_BBMO_clean, select=-c(Sample))
CC_abund_Synd_BBMO_clean_2<-rbind(CC_abund_Synd_BBMO_clean_2,CC_sum)
CC_abund_Synd_BBMO_clean_2<-as.data.frame(CC_abund_Synd_BBMO_clean_2)
# Removal of CCs with null abundance and Sum row
CC_abund_Synd_BBMO_clean_2<-CC_abund_Synd_BBMO_clean_2[,(CC_abund_Synd_BBMO_clean_2[321,]) > 0]
CC_abund_Synd_BBMO_clean_3<-CC_abund_Synd_BBMO_clean_2[1:320,]
# Get genus taxonomic status for selected CCs
CC_id <- data.frame(colnames(CC_abund_Synd_BBMO_clean_3))
names(CC_id)[1]<-"CC_id"
Status<-data.frame(t(Status))
Status$CC_id<-rownames(Status)
Status2<-merge(CC_id,Status)
```


Cross-check sample correspondence between abundance table and metadata

```{r}
# Samples present in metadata but not abundance table
cor1<-anti_join(Metadata_BBMO,CC_abund_Synd_BBMO_clean,by=c("Sample")) # we can use the first abundance table as no sample was removed
#3 samples are present in the metadata table but not in the abundance matrix, we will remove them
Metadata_BBMO<-Metadata_BBMO[which(Metadata_BBMO$Sample %in% CC_abund_Synd_BBMO_clean$Sample),]

# Samples present in abundance table but not metadata
c2<-anti_join(CC_abund_Synd_BBMO_clean,Metadata_BBMO,by=c("Sample"))
```

There is a problem with the samples, there are 86 samples missing in the metadata, it is linked to the replicates (called r3: same date but probably another size fraction), we will recreate the metadata corresponding to those samples.

```{r}
#Store the c2 values 
c2_whitoutR<-c2
#Remove the prefix 'r3' to find the samples in the metadata
c2_whitoutR$Sample<-substr(c2$Sample,1,nchar(c2$Sample)-2)
Metadata_BBMO_withoutR<-Metadata_BBMO
#Remove the prefix 'r2' in the Metadata
Metadata_BBMO_withoutR$Sample<-substr(Metadata_BBMO$Sample,1,nchar(c2$Sample)-2)

#Find the missing samples in the metadata
c2_Metadata<-Metadata_BBMO_withoutR[which(Metadata_BBMO_withoutR$Sample %in% c2_whitoutR$Sample),]
#Check for duplicates 
duplicate<-duplicated(c2_Metadata$Sample)
#Remove the duplicate
c2_Metadata<- c2_Metadata[-which(duplicate==TRUE),]

#Add the 'r3' prefix
c2_Metadata$Sample<-paste(c2_Metadata$Sample,'r3',sep = "")

#Bind ou re-created metadata to our metada table
Metadata_BBMO<-rbind(Metadata_BBMO,c2_Metadata) 

#All good now
c2<-anti_join(CC_abund_Synd_BBMO_clean,Metadata_BBMO,by=c("Sample"))
```


## Application of Hellinger distance to abundances

```{r}
# In order to apply hellinger distance data must be in the format: x=CCs, y=samples (it is the case here)
CC_abund_Synd_BBMO_clean_hel<-decostand((CC_abund_Synd_BBMO_clean_3), method="hellinger")
```

# Addition of temporal info to abundance tables

```{r}
# Set rownames as first column
CC_abund_Synd_BBMO_clean_hel$Sample<-row.names(CC_abund_Synd_BBMO_clean_hel)
# Select temporal data from metadata and merge with abundance table
Metadata_BBMO_temp<-subset(Metadata_BBMO,select=c(Sample,Month,Year))
CC_BBMO_Synd_final<-merge(Metadata_BBMO_temp,CC_abund_Synd_BBMO_clean_hel, by="Sample")
# Pivot final table in order to have samples as rows
CC_BBMO_Synd_final<-pivot_longer(CC_BBMO_Synd_final,!Sample & !Month & !Year,names_to ="CC",values_to="abundance")
names(CC_BBMO_Synd_final)[4]<-"CC_id"
# Add genus taxonomic status
CC_BBMO_Synd_final<-merge(CC_BBMO_Synd_final,Status2,by="CC_id")

```



We then add the seasons to our data, see the structure of the data in terms of month and season coverage, and select the years where the sampling effort allows a complete seasonal coverage for our three datasets.

```{r}

#This function receives a month (x vector) and assigns the corresponding seasons (y vector)

season<-function(x){
  #Creation of a new vector (y) in which we will store the corresponding seasons
  y <- vector(mode = "list", length = length(x))
  #Assignation of the corresponding seasons depending on the month
  for (i in 1:length(x)){
  if (x[i]=='October'| x[i]=='November'|x[i]=='September'){y[i]='Autumn'}
  if (x[i]=='January'|x[i]=='February'|x[i]=='December'){y[i]='Winter'}
  if (x[i]=='April'|x[i]=='May'|x[i]=='March'){y[i]='Spring'}
  if (x[i]=='July'|x[i]=='August'|x[i]=='June'){y[i]='Summer'}
  }
  return(y)
}
```


## Addition of seasonal info to abundance tables

```{r}
#Apply the 'season' function to the data
CC_BBMO_Synd_final$Season<-as.character(season(CC_BBMO_Synd_final$Month))
Metadata_BBMO$Season<-as.character(season(Metadata_BBMO$Month))

#The right order of month
col_order_month<-c("Year","January", "February", "March", "April","May","June","July","August", "September", "October","November", "December")
#Count the number of sample by Year and by month
count_month<-Metadata_BBMO%>% group_by(Month)%>% count(Year)%>% pivot_wider(names_from = "Month", values_from = "n")
#Apply the right order of the month 
count_month<-count_month[,col_order_month]
#See the structure of the data in term of month coverage
print(count_month)

#The right order of seasons 
col_order_season<-c("Year","Spring","Summer","Autumn","Winter")
#Count the number of sample by Year and by seasons 
count_season<-Metadata_BBMO%>% group_by(Season)%>% count(Year)%>% pivot_wider(names_from = "Season", values_from = "n")#Apply the right order of the month 
#Apply the right order of the seasons 
count_season<-count_season[,col_order_season]
#See the structure of the data in term of season coverage
print(count_season)
#Select the year with a total season-coverage 
good_year<-count_season%>% na.omit()%>% select(Year)

#Discard the 'uncomplete' years in the data
Metadata_BBMO<-Metadata_BBMO%>% filter (Year%in%good_year$Year)
CC_BBMO_Synd_final<-CC_BBMO_Synd_final %>% filter (Year%in%good_year$Year)
```

Check if there are Connected Components with null abundance in this new time window
```{r}
#Pivot the dataframe
CC_BBMO_Synd_check<-pivot_wider(CC_BBMO_Synd_final, !Month & !Year & !Genus_status & !Season,names_from = "CC_id", values_from = "abundance")

# Compute sums of CCs abundance
CC_sum<-colSums(CC_BBMO_Synd_check[2:length(CC_BBMO_Synd_check)])
# Set Sample column as rownames, remove Sample column and add of Sum row
rownames(CC_BBMO_Synd_check)<-CC_BBMO_Synd_check$Sample
CC_BBMO_Synd_check_2<-subset(CC_BBMO_Synd_check, select=-c(Sample))
CC_BBMO_Synd_check_2<-rbind(CC_BBMO_Synd_check_2,CC_sum)
CC_BBMO_Synd_check_2<-as.data.frame(CC_BBMO_Synd_check_2)
# Removal of CCs with null abundance and Sum row
CC_BBMO_Synd_check_2<-CC_BBMO_Synd_check_2[,(CC_BBMO_Synd_check_2[321,]) > 0]
CC_BBMO_Synd_check_3<-CC_BBMO_Synd_check_2[1:320,]
#Store the names of the columns
CC_present<-colnames(CC_BBMO_Synd_check_3)

#Filter the final dataframe
CC_BBMO_Synd_final_good<-CC_BBMO_Synd_final[which (CC_BBMO_Synd_final$CC_id %in% CC_present),]

```

Creation of final abundance and metadata tables for BBMO

```{r}
write.csv(CC_BBMO_Synd_final,"CC_abund_Synd_BBMO_clean.csv")
write.csv(Metadata_BBMO,"Metadata_BBMO.csv")
```
