---
title: "data treatment CC Syndinials"
author: "Thomas Finet"
date: "20/05/2022"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, message=FALSE, warning=FALSE, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(dplyr)
library(ggplot2)
library(stringr)
library(tidyverse)
library(openxlsx)
library(readxl)
library(vegan)
library(gridExtra)
library(tidyr)
#Mandatory to us the function 'rbindlist()'
library(data.table)
```

## Syndiniales treated-data importation

Import the hellinger-transformed abundance matrix of Connected Components (CCs) and the metadata.

1/ASTAN
```{r}
CC_abund_Synd_ASTAN_clean<- read.csv("CC_abund_Synd_ASTAN_clean.csv")
#Remove the X column
CC_abund_Synd_ASTAN_clean<-CC_abund_Synd_ASTAN_clean%>% select(-X)
Metadata_ASTAN <- read.csv("Metadata_ASTAN.csv")
#Create a dataframe storing the functional status (i.e. 'Known' or 'Unknwown') of each Connected Components (CCs)
Status_CC_ASTAN<-CC_abund_Synd_ASTAN_clean%>% select(c(CC_id,Genus_status)) %>% unique()

```

2/BBMO

```{r}
CC_abund_Synd_BBMO_clean<- read.csv("CC_abund_Synd_BBMO_clean.csv")
#Remove the X column
CC_abund_Synd_BBMO_clean<-CC_abund_Synd_BBMO_clean%>% select(-X)
Metadata_BBMO <- read.csv("Metadata_BBMO.csv")
#Create a dataframe storing the functional status (i.e. 'Known' or 'Unknwown') of each Connected Components (CCs)
Status_CC_BBMO<-CC_abund_Synd_BBMO_clean%>% select(c(CC_id,Genus_status)) %>% unique()

```

3/SOLA 

```{r}
CC_abund_Synd_SOLA_clean<- read.csv("CC_abund_Synd_SOLA_clean.csv")
#Remove the X column
CC_abund_Synd_SOLA_clean<-CC_abund_Synd_SOLA_clean%>% select(-X)
Metadata_SOLA <- read.csv("Metadata_SOLA.csv")
#Create a dataframe storing the functional status (i.e. 'Known' or 'Unknwown') of each Connected Components (CCs)
Status_CC_SOLA<-CC_abund_Synd_SOLA_clean%>% select(c(CC_id,Genus_status)) %>% unique()

```

##Definition of the functions 

Create three different functions in order to analyse our data :
 
  -TS_year_season: create a list storing each year's abundances.
  -temporality: compute a set of measures to assess the ecological diversity of our dataset.
  -temporality_year: Use the two previous functions to study the differences of presence and abundance between years, using a season-averaged dataset. 

```{r}

#This function divides the dataset according to the years, and then pivots the table. It returns a list of datasets on which the 'temporality' function can be used.

TS_year_season<- function(x){
  #Order the list of the years present in the dataset 
  list_year<-sort(as.numeric(unique(x$Year)))
  #Create an empty list in which we will store our transformed datasets
  table_year<-list()
  #Add year by year the pivoted-data to a list :'table_year')
  for (i in 1:length(list_year)){
  table_year<-append(list(pivot_wider(subset(x,Year==list_year[i]), !Year,names_from = "CC_id", values_from = "abundance")),table_year, 0)
  }
  #Name each file of the 'table_year' list with the year that corresponds
  table_year<-setNames(as.list(table_year),eval(as.character(list_year)))
  
  #return the list of datasets
  return(table_year)
}



#A function that compute different index and measures of interest on an abundance matrix


temporality<-function(y){
  #Convert to dataframe 
  y<-as.data.frame(y)
  #Remove the Sample column
  y<-y[,-1]
  #Transpose our dataframe 
  y_t<-t(y)
  y_t<-as.data.frame(y_t)
  
  #Find the number of seasons in which each CC is present 
  number_season<-specnumber(y_t)
  #Convert to a dataframe
  Presence_sample<-as.data.frame(number_season)
  #Reverse Shannon's index 
  H<-diversity(y_t)
  #Reverse Pielou's index
  J<-H/log(specnumber(y_t))
  #Add the indexes to the `Presence_sample` dataframe 
  Presence_sample$H<-as.numeric(H)
  Presence_sample$J<-as.numeric(J)
  #Convert to numeric
  y[,(1:length(y))] <- sapply(y[,(1:length(y))],as.numeric)
  #Sum of the abundance 
  ab_sum<-colSums(y[,1:length(y)])
  #Add the sum of the abundance to the `Presence_sample` dataframe 
  Presence_sample$ab_sum<-ab_sum
  
  #Mean of the seasonal abundance 
  ab_mean<-colMeans(y[,1:length(y)])
  #Add the mean of the abundance to the `Presence_sample` dataframe 
  Presence_sample$ab_mean<-ab_mean
  
  #Add the status 
  Presence_sample$Status<-Status_CC$Genus_status
  #Add the 'CC_id'
  Presence_sample$CC_id<-Status_CC$CC_id
  return(Presence_sample)
}


#Applying the 'TS_year' and 'temporality' function to a dataset of interest, and then we compute the number of seasons in wich each CC is present, for each year 

temporality_year<-function(y){
  #Compute the mean abundance per season for each CC
  y_clean_Season<- y %>% group_by(CC_id, Year,Season)%>% dplyr::summarize(abundance = mean(abundance, na.rm = TRUE))
  
  #Apply the 'TS_year' function to our raw data (i.e. we convert them to a list format, whith each element of the list containing the seasonal abundances of the CC for a year)
  datasets<-TS_year_season(y_clean_Season)
  results<-list()
  #We apply the temporality function to each year 
  for (i in 1:length(datasets)){
    results<-append(list(temporality(datasets[[i]])),results,0)
  }
  
  #Name each file of the 'results' list with the year that corresponds
  names(results)<-as.character(names(datasets))
  

  #Create a function that we will apply to our list of dataframe to select the columns 'number_season' and 'CC'
  Select<-function (x,col){
    y<-x%>% select(col,CC_id)
    return(y)
  } 
  #Apply the 'Select' function to select the columns of interest (i.e. number_season and CC) in each of the dataframe
  results_common<-lapply(results,Select, col='number_season')
  #Bind all the dataframe of the list (i.e. all the years) and add an Id (i.e. the year)
  results_common_dataframe<-rbindlist(results_common, idcol=TRUE)
  #We pivot the table to have, for each year, the number of seasons present
  results_year<-pivot_wider(results_common_dataframe, names_from = ".id", values_from = "number_season")
  #Count the years to find identical CC in term of season presence 
  results_common_count<-results_common_dataframe%>%group_by(CC_id)%>% count(number_season)
  #Keep the number of seasons that is the most recurrent in the dataset
  max<-results_common_count%>% group_by(CC_id)%>% filter (n==max(n))
  #Identify the CC in double/triple (e.g. 3 years of 2 seasons and 3 years of 1 seasons)
  max_D<-max[duplicated(max$CC_id)| duplicated(max$CC_id, fromLast = TRUE),]
  #Take the minimum value of the doulbe/triple
  max_D_proper<-max_D%>% group_by(CC_id)%>%mutate (number_season=min(number_season))%>% unique()
  #Remove the duplicates from the 'max' file
  max<-max[-which(max$CC_id %in%max_D_proper$CC_id),]
  #Add the new value (i.e. mean) of the deleted rows and order by name
  number_season_max<-rbind(max,max_D_proper)
  
  #Find the years corresponding to the number of seasons selected 
  results_common_dataframe_pivoted<-pivot_wider(results_common_dataframe,names_from = "number_season", values_from = ".id")
  #Merge `results_common_dataframe_pivoted` which contains information on the years and `number_season_max`which contains information on the number of seasons selected 
  number_season_max<-merge(number_season_max,results_common_dataframe_pivoted, by='CC_id')
  
  
  #Create a column `Year` in the 'number_season_max' dataframe
   number_season_max<-number_season_max%>% mutate(Year=0)
   CC_abund_selected<-colnames(CC_abund_Synd_SOLA_clean)
  #fill the column `Year` with the years corresponding to the number of seasons selected and fill it for each CC
  for (i in 1:nrow(number_season_max)){
    #Select the column corresponding to the number in the 'number_season' column and extract from it the years
    number_season_max[i,length(number_season_max)]<-list(number_season_max[i,as.character(number_season_max[i,("number_season")])])
    #Extract the data corresponding to the selected year for each CC in the raw data
    add_CC<-CC_abund_Synd%>% filter(CC_id==number_season_max[i,"CC_id"])%>% subset (Year %in% as.numeric(number_season_max[i,9][[1]]))
    #Compute a new dataframe containing only the data of interest 
    CC_abund_selected<-rbind(CC_abund_selected,add_CC)
  }
  #Remove the first row 
   CC_abund_selected<-CC_abund_selected[-1,]
   
  #Compute the monthly-mean on the period selected for our dataset 
   mean_abundance_month<-CC_abund_selected%>% group_by(CC_id,Month,Year)%>% summarize(mean_abundance_month= mean(as.numeric(abundance)))
  #Compute the yearly-mean of the monthly-mean abundances
   mean_abundance_year<-mean_abundance_month%>% group_by(CC_id,Year)%>% summarize(mean_abundance_year= mean(as.numeric(mean_abundance_month)))
  #Compute the mean of the yearly-mean abundances 
   mean_abundance<-mean_abundance_year%>% group_by(CC_id)%>% summarize(mean_abundance= mean(as.numeric(mean_abundance_year)))
   
   #Merge both
   number_season_max<-merge(number_season_max,mean_abundance, by='CC_id')
   
   #Remove the unnecessary columns 
   number_season_max<-number_season_max%>% select(-c("0","1","2","3","4","Year"))
   #Merge with the number of season presence for each year
   number_season_max<-merge(number_season_max,results_year,by='CC_id')
   
   
   #Compute the monthly_mean for each years of our dataset
   for (i in 1:length(results)){
    #Find the year on which we work
    year_datasets<-as.numeric(names(results[1]))
    #Isolate the year and compute the yearly mean abundance based on the monthly mean for each CC
    mean_abundance_year<-CC_abund_Synd%>%subset(Year==year_datasets)%>% group_by(CC_id,Month)%>% summarize(mean_abundance_month= mean(as.numeric(abundance)))%>% group_by(CC_id)%>% summarize(mean_abundance_year= mean(as.numeric(mean_abundance_month)))
    
    #Add a new column in the list of dataframe 'results' containing the monthly mean called :'mean_abundance_month'
    results[[i]]<-merge(results[[i]],mean_abundance_year, by='CC_id')
   }
  
  #Compute the mean equitability index of our dataset
  
  #Apply the 'Select' function to select the columns of interest (i.e. H, J, abundance and CC) in each of the dataframes
  H_mean<- lapply(results,Select, col='H')
  J_mean<- lapply(results,Select, col='J')
  
  abundance_mean<-lapply(results,Select, col='mean_abundance_year')
  
  #Bind all the dataframes 
  H_mean<- rbindlist(H_mean)
  J_mean<- rbindlist(J_mean)
  abundance_mean<-rbindlist(abundance_mean)
  
  #Compute the mean for each column of interest 
  H_mean<-H_mean%>% group_by(CC_id)%>% summarize(H = mean(H, na.rm = TRUE))
  J_mean<-J_mean%>% group_by(CC_id)%>% summarize(J = mean(J, na.rm = TRUE))
  mean_abundance_all<-abundance_mean%>% group_by(CC_id)%>% summarize(abundance_mean = mean(mean_abundance_year, na.rm = TRUE))
  #rename the abundance column : mean_abundance_all
  colnames(mean_abundance_all)[2]<- "mean_abundance_all"
  
  #Merge the max and H_mean
  All<-merge(H_mean,number_season_max, by='CC_id')
  All<-merge(J_mean,All, by='CC_id')
  All$Status<-Status_CC$Genus_status
  All<-merge(mean_abundance_all,All, by='CC_id')
  #Add the 'All' dataset to the results
  results_with_All<-append(list(All),results, 0)
  #Name the 'All' dataset
  names(results_with_All)[[length(results_with_All)]]<-"All"
  
  #abundances per year 
  
  
  
   return(results_with_All)
}

```




We use the functions described previously to transform our three datasets 

```{r bubbleplot ASTAN}
#Define the 'Status_CC' and the 'CC_abund_Synd' dataframes to the data set that we will use
Status_CC<-Status_CC_ASTAN
CC_abund_Synd<-CC_abund_Synd_ASTAN_clean
#Apply the 'temporality_year' function to the ASTAN dataset
CC_Synd_ASTAN_Bubbleplot<-temporality_year(CC_abund_Synd_ASTAN_clean)

#Extract the 'All' list and convert it to a dataframe 
CC_Synd_ASTAN_All<-as.data.frame(CC_Synd_ASTAN_Bubbleplot['All'])

#Remove the string 'All.' part before each columns name
colnames(CC_Synd_ASTAN_All)<-str_sub(colnames(CC_Synd_ASTAN_All),5)

#Convert the lists in characters

CC_Synd_ASTAN_All[,5:11]<-sapply(CC_Synd_ASTAN_All[,5:11],as.character)

#We export the file
write.csv(CC_Synd_ASTAN_All,"CC_Synd_ASTAN_All.csv")
```

```{r bubbleplot BBMO}
#Define the 'Status_CC' and the 'CC_abund_Synd' dataframes to the data set that we will use
Status_CC<-Status_CC_BBMO
CC_abund_Synd<-CC_abund_Synd_BBMO_clean
#Apply the 'temporality_year' function to the BBMO dataset
CC_Synd_BBMO_Bubbleplot<-temporality_year(CC_abund_Synd_BBMO_clean)
#We export the file 'CC_Synd_BBMO_Bubbleplot'
write.csv(CC_Synd_BBMO_Bubbleplot,"CC_Synd_BBMO_Bubbleplot.csv")


#Extract the 'All' list and convert it to a dataframe 
CC_Synd_BBMO_All<-as.data.frame(CC_Synd_BBMO_Bubbleplot['All'])

#Remove the string 'All.' part before each columns name
colnames(CC_Synd_BBMO_All)<-str_sub(colnames(CC_Synd_BBMO_All),5)

#Convert the lists in characters

CC_Synd_BBMO_All[,5:11]<-sapply(CC_Synd_BBMO_All[,5:11],as.character)

#We export the file 
write.csv(CC_Synd_BBMO_All,"CC_Synd_BBMO_All.csv")
```

```{r bubbleplot SOLA}
#Define the 'Status_CC' and the 'CC_abund_Synd' dataframes to the data set that we will use
Status_CC<-Status_CC_SOLA
CC_abund_Synd<-CC_abund_Synd_SOLA_clean
#Apply the 'temporality_year' function to the SOLA dataset
CC_Synd_SOLA_Bubbleplot<-temporality_year(CC_abund_Synd_SOLA_clean)
#We export the file 'CC_Synd_BBMO_Bubbleplot'
write.csv(CC_Synd_SOLA_Bubbleplot,"CC_Synd_SOLA_Bubbleplot.csv")

#Extract the 'All' list and convert it to a dataframe 
CC_Synd_SOLA_All<-as.data.frame(CC_Synd_SOLA_Bubbleplot['All'])

#Remove the string 'All.' part before each columns name
colnames(CC_Synd_SOLA_All)<-str_sub(colnames(CC_Synd_SOLA_All),5)

#Convert the lists in characters

CC_Synd_SOLA_All[,5:11]<-sapply(CC_Synd_SOLA_All[,5:11],as.character)

#We export the file 
write.csv(CC_Synd_SOLA_All,"CC_Synd_SOLA_All.csv")
```




