---
title: "rhythmicity ASTAN CC"
author: "Thomas Finet"
date: "21/04/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(lomb)
library(readr)
library(dplyr)
library(tibble)
library(tidyr)
```

## Data importation

```{r}
#Import the cleaned data and remove the first column
CC_abund_Synd_ASTAN_clean <- read_csv("CC_abund_Synd_ASTAN_clean.csv")%>% select(-1)
#Import the cleaned Metadata and remove the first column
Metadata_ASTAN <- read_csv("Metadata_ASTAN.csv")%>% select(-1)
#Import the dataframe used to make the bubbleplots and remove the first column
CC_Synd_ASTAN_All <- read_csv("CC_Synd_ASTAN_All.csv")%>% select(-1)
#Import the selected Escouffier's vectors
selection_escoufier_all <- read_csv("selection_escoufier_all_ASTAN.csv")
#Import the RV's of the selected Escouffier's vector 
ASTAN_CC_RV <- read_csv("ASTAN_CC_RV.out", 
    col_names = FALSE)
```

## Merge the Escouffier's selected vectors and their RVs

Select the escouffier'selected vectors and add their RV's, that are in the 'ASTAN_CC_RV' file

```{r}
#Select the names of the escouffier'selected vectors and their order 
selection_escoufier_all<-colnames(selection_escoufier_all)
#Convert to a dataframe 
selection_escoufier_all<-as.data.frame(selection_escoufier_all)
#Remove the order
selection_escoufier_all<-selection_escoufier_all[-1,]
#Convert to a dataframe
selection_escoufier_all<-as.data.frame(selection_escoufier_all)
#Name the column'CC_id'
colnames(selection_escoufier_all)<-"CC_id"
#Put the rownames in a column named 'Escouffier'
selection_escoufier_all<-rownames_to_column(selection_escoufier_all, var="Escouffier")

#Delete the first column
ASTAN_CC_RV<-ASTAN_CC_RV[,-1]
#Rename the column RV
colnames(ASTAN_CC_RV)<-"RV"
#Round the RVs to three digits
ASTAN_CC_RV$RV<-round(as.numeric(substr(ASTAN_CC_RV$RV,5,nchar(ASTAN_CC_RV$RV))),3)
#Remove the last row (because he is not in the vectors selected (as RV>0.75))
ASTAN_CC_RV<-ASTAN_CC_RV[-nrow(ASTAN_CC_RV),]
#Add the Rv column to the 'selection_escoufier_all' dataframe
selection_escoufier_all$RV<-ASTAN_CC_RV$RV
```

We then merge the 'selection_escoufier_all' dataframe, which contains the Escouffier's information of all the CC selected, with the 'CC_Synd_ASTAN_All' dataframe previously computed, which contains information on the seasonal structure of each CC.

```{r}
#Add the Escouffier's vectors 
Table_CC_ASTAN_Synd<-merge(CC_Synd_ASTAN_All,selection_escoufier_all,group_by='CC_id')
#Order according to Escouffier number
Table_CC_ASTAN_Synd<-Table_CC_ASTAN_Synd[order(as.numeric(Table_CC_ASTAN_Synd$Escouffier)),]
#Put Escouffier number before the 'J' column
Table_CC_ASTAN_Synd<-Table_CC_ASTAN_Synd%>% relocate("Escouffier",.before='J')
```


## rhythmicity function

Create a function that compute the periodicity of each Connected Component (CC) and the parameters associated 

```{r}
#A function for the Escouffier's selected CC

rhythmicity<-function (X,Y,Z){
  #Convert the dates in a good format
  d<-as.Date(X$Date,"%d/%m/%Y")
  d<-as.numeric(d)
  #Convert 'd' to a dataframe 
  d<-as.data.frame(d)
  #Compute the time step, by setting the first measure as 0
  d<-d$d-d[1,1]
  #Convert 'd' to a dataframe 
  d<-as.data.frame(d)
  
  #Create the columns that will contain informations regarding the rhythmicity
  Z$PNmax<-0 #PNmax
  Z$Pvalue<-0#Pvalue of the PNmax
  Z$Period<-0#Period of the PNmax
  Z$Periodicity<-0#If it is periodic or not
  
  for (i in 1:nrow(Z)){
    #Find the rank of the abundance dataframe's column that correspond to the CC in the Escouffier's selection
    col_numb<-which(names(Y)==Z[i,1])
    #IASTANte the column
    col<-as.data.frame(Y[,col_numb])[,1]
    #Compute the Lomb Scargle Periodogram using the 'lsp' function
    lsp_1<-lsp(col,times=d$d,type='period',normalize ='press', ofac=5)
    #Compute the summary
    lsp_ASTAN<-summary(lsp_1)
    #Add the PNmax to our final dataframe
    Z[i,'PNmax']<-round(as.numeric(lsp_ASTAN[9,1]),3)
    #Add the P value to our final dataframe
    Z[i,'Pvalue']<-round(as.numeric(lsp_ASTAN[12,1]),4)
    #Add the P value to our final dataframe
    Z[i,'Period']<-round(as.numeric(lsp_ASTAN[10,1]),2)
    #Compute if the CC is periodic or not
    if (Z[i,'PNmax']>10){Z[i,'Periodicity']<-TRUE} 
    else {Z[i,'Periodicity']<-FALSE}
    
  }
  return(Z)
}


```


## Results 

### rhythmicity of the Escouffier's selected CC

We apply the 'rhythmicity' function to the 'Table_CC_ASTAN_Synd' data, i.e. the seasonal information of the CC selected using Escouffier's criterion,  and export the result 

```{r}
#Pivot the dataframe, in order to compute the rhythmicity of the CC
Y<-pivot_wider(CC_abund_Synd_ASTAN_clean, !Month & !Year & !Genus_status & !Season,names_from = "CC_id", values_from = "abundance")
#Order the dataframe in the original chronology
Y<-Y[order(Y$Sample),]
#Apply the 'rhythmicity' function
rhythmicity_ASTAN_final<-rhythmicity (Metadata_ASTAN, Y,Table_CC_ASTAN_Synd)
#Reorder the column
col_order <- c("Escouffier","RV" ,"CC_id","J","H","number_season","n","mean_abundance","2009","2010","2011","2012","2013","2014","2015","2016","Status","PNmax","Pvalue","Period","Periodicity")
#Apply the order of the column to our treated dataframe
rhythmicity_ASTAN_final<-rhythmicity_ASTAN_final[,col_order]
#Export the dataframe 'Rhythmicity_ASTAN_escouf'
write.csv(rhythmicity_ASTAN_final,"Rhythmicity_ASTAN_escouf.csv")
```

### rhythmicity of all the CC

We apply the 'rhythmicity' function to all the CC

```{r}
#Create a dataframe that will store the rhythmicity informations for all the CC
X<-pivot_wider(CC_abund_Synd_ASTAN_clean,  !Month & !Year & !abundance & !Season,names_from = "CC_id", values_from = "Genus_status")
#Transpose it 
X<-t(X[1,-1])
#Convert it to a dataframe 
X<-as.data.frame(X)
#Rename the 'Status' column
colnames(X)<-"Status"
#Create a 'CC_id' column
X<-rownames_to_column(X, var="CC_id")
#Apply the 'rhythmicity' function
rhythmicity_all_ASTAN_final<-rhythmicity (Metadata_ASTAN, Y,X)
#Extract the CC which are periodic
periodic<-rhythmicity_all_ASTAN_final%>% subset(Periodicity==1)%>% select(-"Status")
#Merge with the 'CC_Synd_ASTAN_All' dataframe, which contains seasonal information on the CC. 
Periodic_CC_ASTAN<-merge(periodic,CC_Synd_ASTAN_All, by='CC_id')
#Reorder the column
col_order <- c("CC_id","J","H","number_season","n","mean_abundance","2009","2010","2011","2012","2013","2014","2015","2016","Status","PNmax","Pvalue","Period","Periodicity")
#Apply the order of the column to our treated dataframe
Periodic_CC_ASTAN<-Periodic_CC_ASTAN[,col_order]
#Export the dataframe 'Rhythmicity_CC_ASTAN'
write.csv(Periodic_CC_ASTAN,"Rhythmicity_CC_ASTAN.csv")
```