---
title: "Creation of SSN and selection of parasite clusters"
author: "Iris Rizos"
date: "14/04/2022"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# setwd("/shared/projects/formaldark/R_igraph/Final_files/")

# Import packages
library(igraph)
library(rlist)
library(stringr)
library(plyr)
library(ggplot2)
library(RColorBrewer)
```

## 1. Sequence Similarity Network

# 1.1 Creation and filtering

The network will be composed of nodes connected by edges. The nodes are the metabarcodes and the edges the sequence similarity between them. 

The results of all-against-all blast are the input for the edges of the network. Blast results were filtered according to the following parameters:
Similarity threshold = 100%
Coverage >= 80%

The input file for the nodes is a data-frame containing taxonomic information and metadata of the sequences. Nodes are also called vertices.

```{r eval=FALSE, include=FALSE}
# Read edges and nodes input files
edges=read.csv("SSN_all_filtered_100_cov80.tab", h=F, sep="\t")
nodes=read.csv("All_seq_SSN_tax_status_meta_2.csv", h=T, sep=";")

# Network creation by igraph 
# The graph doesn't have a direction as the edges represent similarity is thus a bidirectional attribute for a pair of sequences  
g <- graph_from_data_frame(d=edges, vertices=nodes, directed = F)

# Check if there are node pairs, a simple graph has only unique pairs
any_multiple(g)
is_simple(g)

# Summary of edges and nodes attributes
summary(g)

# Calculate the network size
gsize(g) # nb edges
gorder(g) # nb nodes

# Remove isolated nodes (sequences not linked to any other sequence at 100% similarity)
isolated = which(degree(g)==0)
length(isolated)
(length(isolated)/count_components(g))*100 # % of isolated nodes
g2 = delete.vertices(g, isolated)

# Save network
# saveRDS(g2, file = "Igraph_100_cov80_noIso.RDS") 
```

# 2.1 Decomposition in clusters

The network is composed of a list of clusters that are generated according to the similarity threshold (here 100%).
These elements are called Connected Components (CCs) and contain sequences that meet the similarity criterium.

When the network is decomposed in clusters, a minimum number of sequences (minimum cluster size) is set. 
Here we apply a cluster threshold size of 6 sequences as our analyses are based on 6 marine regions (defined by a PCA).

```{r}
# Read network
# g2 <- readRDS("Igraph_100_cov80_noIso.RDS")

# Decomposition in CCs
dg <- decompose(g2, mode = c("strong"), max.comps = NA,
                min.vertices = 6)

# Histogram of decomposed CC sizes
comp_sizes = unlist(lapply(dg, function(x) vcount(x)))
comp_sizes <- data.frame(comp_sizes)
sum(comp_sizes)
summary(comp_sizes)
hist(comp_sizes[,1])
```

## 2. Selection of Syndiniales clusters

The majority of unassigned sequences in our global dataset belongs to marine dinoflagellate parasites (Syndiniales or MALVs).

```{r}
# Read 100% similarity network
# dg <- readRDS("Igraph_100_cov80_noIso.RDS")

# Select CCs of Class Syndiniales 
dg_synd <- list()
for (i in dg) {
  t <- table(V(i)$Class)
  t <- data.frame(table(V(i)$Class))
  if (t[1,1] == "Syndiniales" && nrow(t)==1) {
    dg_synd <- list.append(dg_synd,i)
  }
}

# Calculate the % of network represented by Syndiniales
(length(dg_synd)/length(dg))*100 # 34.21%

# Save Syndiniales network
# saveRDS(dg_synd, file = "Igraph_Synd_id100_cov80.RDS") 
```

Among these clusters we can explore the taxonomy. 

# 2.1 How many clusters belong to each Order of Syndiniales ? 

```{r}
# Read Syndiniales network
dg_synd <- readRDS("Igraph_Synd_id100_cov80.RDS")

# Get table with orders of unknown Syndiniales 
######### CC taxonomic info table #########
# Function for order taxonomic status and division group of each CC
#######################################################
###*************************************************###
## For all CC of a graph ##
taxo.info <- function(CC) {
  Tax <- c()
  # Get taxo info
  ord <- V(CC)$Order
  taxonomy <- table(ord)
  taxonomy <- data.frame(taxonomy)
  
  # Create data frame and split genus status and division into 2 columns
  taxonomy <- subset(taxonomy, select = -c(Freq))
  names(taxonomy)[1] <- "Order"
  taxonomy <- taxonomy[1,]
  Tax <- c(Tax,paste(taxonomy))
  
  return(Tax) 
}
###*************************************************###
#######################################################
d = lapply(dg_synd,taxo.info)

# Assign id to each CC of graph 
newlist2 <- mapply(cbind, d, "CC_id"=1:length(dg_synd), SIMPLIFY=F)

# Create data frame
df_taxo <- ldply(newlist2, data.frame)

# Set type of variables
df_taxo$CC_id <- as.character(paste(df_taxo$CC_id))
names(df_taxo)[names(df_taxo)=="V1"] <- "Order"

# We can now calculate the number of CCs among each group
# Distribution of Dino groups
df_I <- df_taxo[df_taxo$Order=="Dino-Group-I",]
CC_I <- nrow(df_I)
df_II <- df_taxo[df_taxo$Order=="Dino-Group-II",]
CC_II <- nrow(df_II)
df_III <- df_taxo[df_taxo$Order=="Dino-Group-III",]
CC_III <- nrow(df_III)
df_IV <- df_taxo[df_taxo$Order=="Dino-Group-IV",]
CC_IV <- nrow(df_IV)
df_V <- df_taxo[df_taxo$Order=="Dino-Group-V",]
CC_V <- nrow(df_V)
df_uk <- df_taxo[df_taxo$Order=="Unknown",]
CC_uk <- nrow(df_uk)

# Create data-frame
tax_status <- c("Dino-Group-I","Dino-Group-II","Dino-Group-III","Dino-Group-IV","Dino-Group-V","Unknown")
CC_nb <- c(CC_I,CC_II,CC_III,CC_IV,CC_V,CC_uk)
df <- data.frame(tax_status, CC_nb)

# Plot
p1 <- ggplot(df, aes(y=CC_nb, x=tax_status,fill=tax_status)) + 
  geom_bar(stat="identity", colour="black") +
  scale_fill_brewer(palette="Dark2") +
  theme_classic() +
  theme(axis.ticks.x=element_blank(), axis.title.x=element_blank(), axis.text.x=element_text(face="bold")) +
  ylab("Number of CCs") +
  labs(fill='Syndiniales Order') +
  theme(legend.title = element_text(face="bold")) +
  geom_text(aes(label=CC_nb), position=position_dodge(width=0.9), vjust=-0.25) +
  ggtitle("Syndiniales clusters: assigned and unassigned") +
  theme(plot.title = element_text(hjust=0.5, face="bold"))

plot(p1)
```

# 2.2 What is their size and how many contain unassigned sequences ?
We select only Syndiniales clusters that do not have a taxonomic annotation at genus level.

Figure S7 A,B

```{r}
# Calculate CC size
comp_sizes = unlist(lapply(dg_synd, function(x) vcount(x)))
comp_sizes <- data.frame(comp_sizes,stringsAsFactors = T)
CC_id <- row.names(comp_sizes)
comp_sizes <- cbind(comp_sizes, CC_id)

# Function for genus taxonomic status of each CC
#######################################################
###*************************************************###
## For all CC of a graph ##
taxo.info.genus <- function(CC) {
  Tax <- c()
  # Get taxo info
  gen <- V(CC)$Genus_status
  taxonomy <- table(gen)
  taxonomy <- data.frame(taxonomy)
  
  # Create data frame and split genus status and division into 2 columns
  taxonomy <- subset(taxonomy, select = -c(Freq))
  names(taxonomy)[1] <- "Genus"
  taxonomy <- taxonomy[1,]
  Tax <- c(Tax,paste(taxonomy))
  
  return(Tax) 
}
###*************************************************###
#######################################################
d = lapply(dg_synd,taxo.info.genus)

# Assign id to each CC of graph 
newlist2 <- mapply(cbind, d, "CC_id"=1:length(dg_synd), SIMPLIFY=F)

# Create data frame
df_taxo <- ldply(newlist2, data.frame)
summary(df_taxo)

# Set type of variables
df_taxo$CC_id <- as.character(paste(df_taxo$CC_id))
names(df_taxo)[names(df_taxo)=="V1"] <- "Genus"

# Merge with CC sizes
data <- merge(comp_sizes, df_taxo, by="CC_id")
data_uk <- data[data$Genus=="Unknown",]
data_uk[data_uk=="Unknown"] <- "Unassigned"
data_k <- data[data$Genus=="Known",]

# Histogram of CC size distribution according to genus taxonomic assignment (Fig S7A)
g1 <- ggplot(data_uk, aes(fill=Genus, x=comp_sizes)) +
  geom_histogram(binwidth=1,aes(fill=Genus)) +
  scale_fill_manual(values=c("black")) +
  theme_bw() +
  xlab("CC size (nb of sequences)") +
  ylab("CC count (nb)")

g2 <- ggplot(data_k, aes(fill=Genus, x=comp_sizes)) +
  geom_histogram(binwidth=1,aes(fill=Genus)) +
  scale_fill_manual(values=c("red")) +
  theme_bw() +
  xlab("CC size (nb of sequences)") +
  ylab("CC count (nb)")

grid.arrange(g1,g2)

####### Fig S7 B

# Select CCs unassigned at genus level
dg_synd_uk <- list()
for (i in dg_synd) {
  t <- table(V(i)$Genus_status)
  t <- data.frame(table(V(i)$Genus_status))
  if (t[1,1] == "Unknown" && nrow(t)==1) {
    dg_synd_uk <- list.append(dg_synd_uk,i)
  }
}

# Calculate the % of Syndiniales network represented by unassigned Syndiniales
(length(dg_synd_uk)/length(dg_synd))*100

# Select CCs of Unassigned Genus 
dg_uk <- list()
for (i in dg) {
  t <- table(V(i)$Genus)
  t <- data.frame(table(V(i)$Genus))
  if (t[1,1] == "Unknown" && nrow(t)==1) {
    dg_uk <- list.append(dg_uk,i)
  }
}

# Calculate the % that unassigned Syndiniales represent from all unassigned microbiome network
(length(dg_synd_uk)/length(dg_uk))*100

# Taxonomy data of unassigned syndiniales at order level
d = lapply(dg_synd_uk,taxo.info)

# Assign id to each CC of graph 
newlist2 <- mapply(cbind, d, "CC_id"=1:length(dg_synd_uk), SIMPLIFY=F)

# Create data frame
df_taxo <- ldply(newlist2, data.frame)

# Set type of variables
df_taxo$CC_id <- as.character(paste(df_taxo$CC_id))
names(df_taxo)[names(df_taxo)=="V1"] <- "Order"

# We can now calculate the number of CCs among each group
# Distribution of Dino groups
df_I <- df_taxo[df_taxo$Order=="Dino-Group-I",]
CC_I <- nrow(df_I)
df_II <- df_taxo[df_taxo$Order=="Dino-Group-II",]
CC_II <- nrow(df_II)
df_III <- df_taxo[df_taxo$Order=="Dino-Group-III",]
CC_III <- nrow(df_III)
df_IV <- df_taxo[df_taxo$Order=="Dino-Group-IV",]
CC_IV <- nrow(df_IV)
df_V <- df_taxo[df_taxo$Order=="Dino-Group-V",]
CC_V <- nrow(df_V)
df_uk <- df_taxo[df_taxo$Order=="Unknown",]
CC_uk <- nrow(df_uk)

# Create data-frame
tax_status <- c("Dino-Group-I","Dino-Group-II","Dino-Group-III","Dino-Group-IV","Dino-Group-V","Unknown")
CC_nb <- c(CC_I,CC_II,CC_III,CC_IV,CC_V,CC_uk)
df <- data.frame(tax_status, CC_nb)

# Plot
p2 <- ggplot(df, aes(y=CC_nb, x=tax_status,fill=tax_status)) + 
  geom_bar(stat="identity", colour="black") +
  scale_fill_brewer(palette="Dark2") +
  theme_classic() +
  theme(axis.ticks.x=element_blank(), axis.title.x=element_blank(), axis.text.x=element_text(face="bold")) +
  ylab("Number of CCs") +
  labs(fill='Syndiniales Order') +
  theme(legend.title = element_text(face="bold")) +
  geom_text(aes(label=CC_nb), position=position_dodge(width=0.9), vjust=-0.25) +
  ggtitle("Syndiniales clusters: unassigned") +
  theme(plot.title = element_text(hjust=0.5, face="bold"))

plot(p2)
```

