---
title: "Temporality_Supplementary Materials"
author: "Thomas Finet"
date: "12/07/2022"
output: html_document
---

```{r }
knitr::opts_chunk$set(echo = TRUE)

library(ggplot2)
library(dplyr)
library (readr)
```



################################################################  ASTAN  ######################################################



Import the hellinger-transformed abundance matrix of Connected Components (CCs)

```{r}
CC_abund_Synd_ASTAN_clean <- read_csv("C:/Users/thoma/OneDrive/Bureau/Script Article Iris/Mat_Sup/CC_abund_Synd_ASTAN_clean.csv")
CC_abund_Synd_ASTAN_clean<-CC_abund_Synd_ASTAN_clean[,-1]

```

Import the rythmic and escouffier-selected CC
```{r}
Rhythmicity_ASTAN_final <- read_csv("C:/Users/thoma/OneDrive/Bureau/Script Article Iris/Mat_Sup/Rhythmicity_ASTAN_final.csv")
Rhythmicity_ASTAN_final<-Rhythmicity_ASTAN_final[,-1]
```

Import the treated data
```{r}
CC_Synd_ASTAN_All <- read_csv("C:/Users/thoma/OneDrive/Bureau/Script Article Iris/Mat_Sup/CC_Synd_ASTAN_All.csv")
CC_Synd_ASTAN_All<-CC_Synd_ASTAN_All[,-1]
```

#Processing
For each CC, we compute a monthly mean by year, and then the mean of the yearly-month mean
```{r}
CC_abund_Synd_ASTAN_clean_YM_mean<-CC_abund_Synd_ASTAN_clean%>% group_by(CC_id, Month,Year)%>% summarize(mean_abundance_month_year= mean(abundance))
CC_abund_Synd_ASTAN_clean_Y_mean<-CC_abund_Synd_ASTAN_clean_YM_mean%>%group_by(CC_id,Month)%>% summarize(mean_abundance_year= mean(mean_abundance_month_year))
```

Filter the Rhythmicity table to only keep the rythmic CC, which has a coherent period (less than the length of the time serie)

```{r}
Rhythmicity_ASTAN_final<-Rhythmicity_ASTAN_final%>% filter(Periodicity==1)%>% filter(Period<2900)
```

We then add the genus status, if they are rythmic and selected using the escouffier criterion

```{r}
#Isolate the Genus_status 
Status<-CC_abund_Synd_ASTAN_clean%>% select(CC_id,Genus_status)%>% unique()

#Add the Rhythmicity/escouffier informations

#Creat a new column
Status$Rythmic<-0
#Add the value one when the CC is in the escouffier/Rhythmicity table
Status[which(Status$CC_id%in%(Rhythmicity_ASTAN_final$CC_id)),"Rythmic"]<-1
#We merge both datasets
CC_abund_Synd_ASTAN_clean_monthlyplot<-merge(CC_abund_Synd_ASTAN_clean_Y_mean,Status,by="CC_id")

```

## Plot

We create boxplots by using the log-transformed abundances mean by month for the known and unknown CC. 

```{r plot}
plot<- ggplot (data=CC_abund_Synd_ASTAN_clean_monthlyplot, aes (x=Month,y=log(mean_abundance_year), fill=Genus_status))+ 
  geom_boxplot()
plot+theme_classic()+
  scale_fill_manual(values=c('firebrick','gray33')) +
  scale_x_discrete(limits = c("January", "February", "March", "April","May","June","July","August", "September", "October","November", "December"))+
#Add the rythmic and escouffier selected CC abundances in each month
  geom_dotplot(filter(CC_abund_Synd_ASTAN_clean_monthlyplot,Rythmic==1),mapping=aes (x=Month,y=log(mean_abundance_year)),binaxis='y', binpositions="all",binwidth=0.14)
```





################################################################  BBMO  ######################################################




Import the hellinger-transformed abundance matrix of Connected Components (CCs)

```{r}
CC_abund_Synd_BBMO_clean <- read_csv("C:/Users/thoma/OneDrive/Bureau/Script Article Iris/Mat_Sup/CC_abund_Synd_BBMO_clean.csv")
CC_abund_Synd_BBMO_clean<-CC_abund_Synd_BBMO_clean[,-1]

```

Import the rythmic and escouffier-selected CC
```{r}
Rhythmicity_BBMO_final <- read_csv("C:/Users/thoma/OneDrive/Bureau/Script Article Iris/Mat_Sup/Rhythmicity_BBMO_final.csv")
Rhythmicity_BBMO_final<-Rhythmicity_BBMO_final[,-1]
```

Import the treated data
```{r}
CC_Synd_BBMO_All <- read_csv("C:/Users/thoma/OneDrive/Bureau/Script Article Iris/Mat_Sup/CC_Synd_BBMO_All.csv")
CC_Synd_BBMO_All<-CC_Synd_BBMO_All[,-1]
```

#Processing
For each CC, we compute a monthly mean by year, and then the mean of the yearly-month mean
```{r}
CC_abund_Synd_BBMO_clean_YM_mean<-CC_abund_Synd_BBMO_clean%>% group_by(CC_id, Month,Year)%>% summarize(mean_abundance_month_year= mean(abundance))
CC_abund_Synd_BBMO_clean_Y_mean<-CC_abund_Synd_BBMO_clean_YM_mean%>%group_by(CC_id,Month)%>% summarize(mean_abundance_year= mean(mean_abundance_month_year))
```

Filter the Rhythmicity table to only keep the rythmic CC, which has a coherent period (less than the length of the time serie)

```{r}
Rhythmicity_BBMO_final<-Rhythmicity_BBMO_final%>% filter(Periodicity==1)%>% filter(Period<2900)
```

We then add the genus status, if they are rythmic and selected using the escouffier criterion

```{r}
#Isolate the Genus_status 
Status<-CC_abund_Synd_BBMO_clean%>% select(CC_id,Genus_status)%>% unique()

#Add the Rhythmicity/escouffier informations

#Creat a new column
Status$Rythmic<-0
#Add the value one when the CC is in the escouffier/Rhythmicity table
Status[which(Status$CC_id%in%(Rhythmicity_BBMO_final$CC_id)),"Rythmic"]<-1
#We merge both datasets
CC_abund_Synd_BBMO_clean_monthlyplot<-merge(CC_abund_Synd_BBMO_clean_Y_mean,Status,by="CC_id")

```

## Plot

We create boxplots by using the log-transformed abundances mean by month for the known and unknown CC. 

```{r plot}
plot<- ggplot (data=CC_abund_Synd_BBMO_clean_monthlyplot, aes (x=Month,y=log(mean_abundance_year), fill=Genus_status))+ 
  geom_boxplot()
plot+theme_classic()+
  scale_fill_manual(values=c('firebrick','gray33')) +
  scale_x_discrete(limits = c("January", "February", "March", "April","May","June","July","August", "September", "October","November", "December"))+
#Add the rythmic and escouffier selected CC abundances in each month
  geom_dotplot(filter(CC_abund_Synd_BBMO_clean_monthlyplot,Rythmic==1),mapping=aes (x=Month,y=log(mean_abundance_year)),binaxis='y', binpositions="all",binwidth=0.14)
```


################################################################  SOLA  ######################################################


Import the hellinger-transformed abundance matrix of Connected Components (CCs)

```{r}
CC_abund_Synd_SOLA_clean <- read_csv("C:/Users/thoma/OneDrive/Bureau/Script Article Iris/Mat_Sup/CC_abund_Synd_SOLA_clean.csv")
CC_abund_Synd_SOLA_clean<-CC_abund_Synd_SOLA_clean[,-1]

```

Import the rythmic and escouffier-selected CC
```{r}
Rhythmicity_SOLA_final <- read_csv("C:/Users/thoma/OneDrive/Bureau/Script Article Iris/Mat_Sup/Rhythmicity_SOLA_final.csv")
Rhythmicity_SOLA_final<-Rhythmicity_SOLA_final[,-1]
```

Import the treated data
```{r}
CC_Synd_SOLA_All <- read_csv("C:/Users/thoma/OneDrive/Bureau/Script Article Iris/Mat_Sup/CC_Synd_SOLA_All.csv")
CC_Synd_SOLA_All<-CC_Synd_SOLA_All[,-1]
```

#Processing
For each CC, we compute a monthly mean by year, and then the mean of the yearly-month mean
```{r}
CC_abund_Synd_SOLA_clean_YM_mean<-CC_abund_Synd_SOLA_clean%>% group_by(CC_id, Month,Year)%>% summarize(mean_abundance_month_year= mean(abundance))
CC_abund_Synd_SOLA_clean_Y_mean<-CC_abund_Synd_SOLA_clean_YM_mean%>%group_by(CC_id,Month)%>% summarize(mean_abundance_year= mean(mean_abundance_month_year))
```

Filter the Rhythmicity table to only keep the rythmic CC, which has a coherent period (less than the length of the time serie)

```{r}
Rhythmicity_SOLA_final<-Rhythmicity_SOLA_final%>% filter(Periodicity==1)%>% filter(Period<2900)
```

We then add the genus status, if they are rythmic and selected using the escouffier criterion

```{r}
#Isolate the Genus_status 
Status<-CC_abund_Synd_SOLA_clean%>% select(CC_id,Genus_status)%>% unique()

#Add the Rhythmicity/escouffier informations

#Creat a new column
Status$Rythmic<-0
#Add the value one when the CC is in the escouffier/Rhythmicity table
Status[which(Status$CC_id%in%(Rhythmicity_SOLA_final$CC_id)),"Rythmic"]<-1
#We merge both datasets
CC_abund_Synd_SOLA_clean_monthlyplot<-merge(CC_abund_Synd_SOLA_clean_Y_mean,Status,by="CC_id")

```

## Plot

We create boxplots by using the log-transformed abundances mean by month for the known and unknown CC. 

```{r plot}
plot<- ggplot (data=CC_abund_Synd_SOLA_clean_monthlyplot, aes (x=Month,y=log(mean_abundance_year), fill=Genus_status))+ 
  geom_boxplot()
plot+theme_classic()+
  scale_fill_manual(values=c('firebrick','gray33')) +
  scale_x_discrete(limits = c("January", "February", "March", "April","May","June","July","August", "September", "October","November", "December"))+
#Add the rythmic and escouffier selected CC abundances in each month
  geom_dotplot(filter(CC_abund_Synd_SOLA_clean_monthlyplot,Rythmic==1),mapping=aes (x=Month,y=log(mean_abundance_year)),binaxis='y', binpositions="all",binwidth=0.14)
```
